\Large On-Shell Methods for Tree-Level Amplitudes in (De)Constructed Gauge Theory

### 2025-06-25 2nd report/2report.tex
New

\documentclass{beamer}
\usetheme{Madrid}
\usefonttheme{professionalfonts}
\usecolortheme{rose}
\usepackage{fontspec}
\setmainfont{Times New Roman}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{enumitem}
\usepackage{bm}
\usepackage{booktabs}
\usepackage{tikz}
\usepackage{svg}
\usepackage{graphics}
\usepackage{appendixnumberbeamer}
\usepackage{mathtools}
\usepackage{subcaption}
\usepackage{comment}
\usepackage{slashed}
\usepackage[most]{tcolorbox}
\usepackage{tikz}
\usepackage{cancel}
\usetikzlibrary{calc}
\usetikzlibrary{arrows.meta, positioning}

\setlist[enumerate]{label=\arabic*.}
\setlist[itemize]{label=\textbullet}  % 标准 bullet 点
\tcbset{
  thickitembox/.style={
    colback=white,
    colframe=white,
    left=2mm,
    before skip=4pt,
    after skip=4pt,
    borderline west={3pt}{0pt}{gray},  % ← 这里控制线条粗细和颜色
    enhanced,
  }
}
\usetikzlibrary{decorations.pathreplacing}
\usetikzlibrary{arrows.meta}
\setlength{\parskip}{0.3em}
\newcommand{\aket}[1]{|#1\rangle}
\newcommand{\sket}[1]{|#1]}
\newcommand{\avg}[1]{\langle #1 \rangle}
\newcommand{\mdavg}[2]{\langle #1 \rangle\!\langle #2 \rangle}
\newcommand{\asqu}[1]{{\langle#1\rangle}^2}
\newcommand{\tif}[1]{\textit{\textbf{#1}}}
\newcommand{\cbrak}[2]{\avg{#1}\![#2]}
\newcommand{\acbrak}[2]{[#1]\!\avg{#2}}
\AtBeginSection[]{
\begin{frame} 
    \frametitle{Contents}
    \tableofcontents[currentsection]
\end{frame}
}
\title[Application of BCFW]{\Large On-Shell Methods for Tree-Level Amplitudes in (De)Constructed Gauge Theory}
\author[Su Yingze]{
  \textbf{Su Yingze}\\[0.2em]
  \small Supervisor: \tif{Prof. Tanabashi Masaharu}
}

\institute[E Lab]{
  \normalsize Theoretical Elementary Particle Physics Laboratory\\[-0.3em]
  Nagoya University
}

\date[$11^{\text{th}}$ June]{June 11th, 2025}

@@

\end{frame}
\section{Preliminary}
\begin{frame}
\frametitle{Modern Amplitude Method} 
 The answer is On-shell method.
    \begin{center}

@@

    \qquad \textbf{Parke–Taylor Formula (MHV amplitudes):}
    \begin{align*}
    A_5[1^+2^+3^+4^+5^+] &= 0 
    \qquad (\!+,-:~\text{\hyperlink{helicity}{helicity};} \\
    A_5[1^-2^+3^+4^+5^+] &= 0 
    \qquad 1,2,\cdots,n:~\text{particle labels}) \\
    \end{align*}
    \vspace{-3em}
    \hypertarget{conv}{}
    \pause
    \begin{gather*}
        {A_5[1^-2^-3^-4^-5^-]=0}\\
        {A_5[1^+2^-3^-4^-5^-]=0}\\
        \textcolor{red}{A_5[1^+2^+3^-4^-5^-]=\frac{[12]^4}{[12][23][34][45][51]}}
    \end{gather*}
\end{frame}

\begin{frame}
    \frametitle{Color-ordering for Yang-Mills}
    Consider the Yang-Mills lagrangian
    \begin{equation*}
        \mathcal{L}=-\frac{1}{2}\mathrm{Tr}(F_{\mu\nu}F^{\mu\nu})
    \end{equation*}
    The 3 point and 4 point vertices include $\tilde{f}^{abc}$ and $\tilde{f}^{abe}\tilde{f}^{cde}+\text{perms}$.

@@

\begin{frame}
    From Cauchy Theorem, we can ontain
    \begin{equation*}
        A_n=-\sum_{z_I}\textrm{Res}|_{z=z_I}\frac{\hat{A}_n(z)}{z}+B_n,
    \end{equation*}
    where $B_n$ is the residue of the pole at $z=\infty$, called boundary term.
    \vspace{-1em}
    \begin{figure}[htbp]
        \centering
        \includegraphics[width=0.3\textwidth]{CT.png}
    \end{figure}
    \vspace{-1.5em}
    %Then, at a $z_I$ pole, the propagator $\hat{P}_I^2$ goes to on-shell. In that limit, the shifted amplitude
    %\textcolor{red}{factorizes} into to on-shell parts (Unitarity)
    \begin{equation*}
        \hat{A}_n(z)\quad \xrightarrow{z\,\text{near}\,z_I} \quad \hat{A}_L(z_I)\frac{1}{\hat{P}_I^2}\hat{A}_R(z_I)= - \frac{z_I}{z-z_I}\hat{A}_L(z_I)\frac{1}{P_I^2}\hat{A}_R(z_I)
    \end{equation*}
    This makes it easy to evaluate the residue at $z=z_I$
    \begin{equation*}
        -\mathrm{Res}|_{z=z_I}\frac{\hat{A}_n(z)}{z}=\frac{(z-z_I)z_I}{z(z-z_I)}\hat{A}_L(z_I)\frac{1}{P_I^2}\hat{A}_R(z_I)|_{z=z_I}=\hat{A}_L(z_I)\frac{1}{P_I^2}\hat{A}_R(z_I)
    \end{equation*}
\end{frame}

>>>>

\documentclass{beamer}
\usetheme{Madrid}
\usefonttheme{professionalfonts}
\usecolortheme{rose}
\usepackage{fontspec}
\setmainfont{Times New Roman}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{enumitem}
\usepackage{bm}
\usepackage{booktabs}
\usepackage{tikz}
\usepackage{svg}
\usepackage{graphics}
\usepackage{appendixnumberbeamer}
\usepackage{mathtools}
\usepackage{subcaption}
\usepackage{comment}
\usepackage{slashed}
\usepackage[most]{tcolorbox}
\usepackage{tikz}
\usepackage{cancel}
\usepackage{newtxtext,newtxmath}
\usetikzlibrary{calc}
\usetikzlibrary{arrows.meta, positioning}

\setlist[enumerate]{label=\arabic*.}
\setlist[itemize]{label=\textbullet}  % 标准 bullet 点
\tcbset{
  thickitembox/.style={
    colback=white,
    colframe=white,
    left=2mm,
    before skip=4pt,
    after skip=4pt,
    borderline west={3pt}{0pt}{gray},  % ← 这里控制线条粗细和颜色
    enhanced,
  }
}
\usetikzlibrary{decorations.pathreplacing}
\usetikzlibrary{arrows.meta}
\setlength{\parskip}{0.3em}
\newcommand{\aket}[1]{|#1\rangle}
\newcommand{\sket}[1]{|#1]}
\newcommand{\avg}[1]{\langle #1 \rangle}
\newcommand{\mdavg}[2]{\langle #1 \rangle\!\langle #2 \rangle}
\newcommand{\asqu}[1]{{\langle#1\rangle}^2}
\newcommand{\tif}[1]{\textit{\textbf{#1}}}
\newcommand{\cbrak}[2]{\avg{#1}\![#2]}
\newcommand{\acbrak}[2]{[#1]\!\avg{#2}}
\AtBeginSection[]{
\begin{frame} 
    \frametitle{Contents}
    \tableofcontents[currentsection]
\end{frame}
}
\title[Application of BCFW]{\Large On-Shell Methods for Tree-Level Amplitudes in (De)Constructed Gauge Theory}
\author[Su Yingze]{
  \textbf{Su Yingze}
}

\institute[E Lab]{
  \normalsize E Lab, Nagoya University
}

\date[$1^{\text{st}}$ July]{July 1st, 2025}

@@

\end{frame}
\section{Preliminary}
\begin{frame}
    \frametitle{Analyticity}
    Amplitudes are analytic functions
    \begin{itemize}
        \item Tree level scattering amplitudes are rational functions of Lorentz invariants, such as $\bm{p_{i\mu}p_j^\mu}$, $\bm{p_{i\mu}\epsilon_j^\mu}$.
        \item \textbf{Locality} tells us that any pole of a tree-level amplitude must correspond to a on-shell propagating particle. 
        \item There's only single pole, no branch cuts (logs, square roots, etc) at tree level.
\end{itemize}
Historically, when people consider 4-point scattering 
\begin{equation*}
    p_1,p_2,p_3,p_4, \quad \text{satisfying}\quad p_i^2=0 \quad\text{and}\quad \sum_{i=1}^{4}p_i=0
\end{equation*}
\begin{equation*}
    \text{d.o.f}=4n-4-n=3n-4\quad \text{independent complexed d.o.f}
\end{equation*}
This seems to be too much, so people change to use Mandelstam variables
\begin{equation*}
    s,t,u(\text{for}~~\pi\pi~~\text{scattering})\quad\text{satisfying}\quad s+t+u=0
\end{equation*}
\end{frame}

\begin{frame}
    Also for earliest String Amplitude (Venezaino Amplitude)
    \begin{equation*}
        A_{\text{open}}(s, t) = g^2 \frac{\Gamma(-\alpha' s)\, \Gamma(-\alpha' t)}{\Gamma(-\alpha' s - \alpha' t)}
    \end{equation*}
   But the problem is that Mandelstam variables only apply to 2$\rightarrow$2 scattering, how about higher point?
   \begin{equation*}
    \text{single complexed variable like}\quad A(z) 
   \end{equation*}
   This is the starting point of BCFW recursion relation!
\end{frame}

\begin{frame}
    \frametitle{Poincaré Invariance and Little Group Scaling }
    We consider a Poincaré invariant field theory.
    The one-particle state are defined from a reference momentum k like this  
    \begin{equation*}
         \aket{p;\sigma}=U(L(p;k))\aket{k;\sigma}
    \end{equation*}
    Then the general Lorentz transformation acts like
    \begin{align*}
        U(\Lambda)|p,\sigma\rangle &= U(\Lambda) U(L(p;k))|k,\sigma \rangle \\
        &= U(L(\Lambda p;k)) U(L^{-1}(\Lambda p;k) \Lambda L(p;k)) |k,\sigma \rangle\
    \end{align*}
    here $W=L^{-1}(\Lambda p;k) \Lambda L(p;k)$ is not a general transformation but keep k invariant, called little group.
    Thus we have 
    \begin{equation*}
         U(W(\Lambda,p,k))\aket{k;\sigma}=D_{\sigma\sigma^{'}}(W(\Lambda,p,k))\aket{k,\sigma^{'}}
    \end{equation*}
    so one-particle state with momentum p transformed like 
    \begin{equation*}
        \textcolor{red}{U(\Lambda)|p,\sigma\rangle=D_{\sigma\sigma^{'}}(W(\Lambda,p,k))\aket{\Lambda p,\sigma^{'}}}
    \end{equation*}
\end{frame}

\begin{frame}
    \textcolor{red}{One-particle state transformed under the little group!}

    For massless particle, the little group is $SO(2)\backsimeq U(1)$, so the representation matrix is just a phase.
    The Poincaré invariance of S-matrix requires 
    \begin{equation*}
        \mathcal{M}^\Lambda(p_a,\sigma_a)=\prod_{a}(D_{\sigma\sigma^{'}})\mathcal{M}((\Lambda p)_a,\sigma_a^{'})
    \end{equation*}
      \begin{itemize}
        \item $\textbf{\text{Massless Case}}$\\
    \begin{equation*}
        p_\mu \sigma^\mu=p_{\alpha\dot{\alpha}}=\lambda_\alpha \tilde{\lambda}_{\dot{\alpha}}=\aket{\lambda}[\lambda|
    \end{equation*}
    There is an ambiguity for the definition, the momentum is invariant under the following redefinition
    \begin{equation*}
        \lambda \rightarrow t^{-1}\lambda, \qquad \tilde{\lambda}\rightarrow t\tilde{\lambda}, \qquad t\in\mathbb{C} 
    \end{equation*}
    same for
    \begin{equation*}
        \aket{\lambda}\rightarrow t^{-1}\aket{\lambda}, \qquad \sket{\lambda}\rightarrow t\sket{\lambda}
    \end{equation*}
    The scattering amplitudes should transform \textcolor{red}{covariantly} under little group scaling:
    \begin{equation*}
        \color{red} \mathcal{A}_n(\{\aket{1},\sket{1},h_1\},\ldots\{t_i^{-1}\aket{i},t_i\sket{i},h_i\},\ldots )=t_i^{2h_i}\mathcal{A}_n
    \end{equation*}
    \end{itemize}
\end{frame}

\begin{frame}
    \frametitle{Crossing Symmetry and MHV Classification}
    Crossing symmetry is a result from analyticity, unitarity and Lorentz invariance. 
    \begin{figure}
        \centering
        \includegraphics[width=0.6\textwidth]{CrossingSYM.png}
    \end{figure}
\end{frame}

\begin{frame}
\frametitle{Modern Amplitude Method} 
 The answer is On-shell method.
    \begin{center}

@@

    \qquad \textbf{Parke–Taylor Formula (MHV amplitudes):}
    \begin{align*}
    A_5[1^+2^+3^+4^+5^+] =& 0 
    \qquad (\!+,-:~\text{\hyperlink{helicity}{helicity};} \\
    A_5[1^-2^+3^+4^+5^+] =& 0 
    \qquad 1,2,\cdots,n:~\text{particle labels}) \\
    \textcolor{red}{A_5[1^-2^-3^+4^+5^+]} &=\frac{\langle 1 2 \rangle^4}{\langle 1 2 \rangle \langle 2 3 \rangle  \langle 3 4 \rangle \langle 4 5 \rangle \langle 5 1 \rangle}\quad (\text{first non-trival one})
    \end{align*}
    \vspace{-1em}
    \hypertarget{conv}{}
    \pause
    \begin{gather*}
        {A_5[1^-2^-3^-4^-5^-]=0}\\
        {A_5[1^+2^-3^-4^-5^-]=0}\\
        \textcolor{red}{A_5[1^+2^+3^-4^-5^-]=\frac{[12]^4}{[12][23][34][45][51]}}
    \end{gather*}
\end{frame}

\begin{frame}
    \frametitle{Color-ordering for Yang-Mills}
    Consider the Yang-Mills Lagrangian
    \begin{equation*}
        \mathcal{L}=-\frac{1}{2}\mathrm{Tr}(F_{\mu\nu}F^{\mu\nu})
    \end{equation*}
    The 3 point and 4 point vertices include $\tilde{f}^{abc}$ and $\tilde{f}^{abe}\tilde{f}^{cde}+\text{perms}$.

@@

\begin{frame}
   The most important point here is that
    \begin{equation*}
        \boxed{\color{red}\mathrm{Res}|_{z=0}\frac{\hat{A}_n(z)}{z}=\hat{A}_n(0)=A_n}
    \end{equation*}
    It means that the original amplitude equals to the residue at origin.
    \vspace{-1em}
    \begin{figure}[htbp]
        \centering
        \includegraphics[width=0.3\textwidth]{CT.png}
    \end{figure}
    \vspace{-1.5em}
    %Then, at a $z_I$ pole, the propagator $\hat{P}_I^2$ goes to on-shell. In that limit, the shifted amplitude
    %\textcolor{red}{factorizes} into to on-shell parts (Unitarity)
    \begin{equation*}
        \hat{A}_n(z)\quad \xrightarrow{z\,\text{near}\,z_I} \quad \hat{A}_L(z_I)\frac{1}{\hat{P}_I^2}\hat{A}_R(z_I)= - \frac{z_I}{z-z_I}\hat{A}_L(z_I)\frac{1}{P_I^2}\hat{A}_R(z_I)
    \end{equation*}
    This makes it easy to evaluate the residue at $z=z_I$
    \begin{equation*}
        -\mathrm{Res}|_{z=z_I}\frac{\hat{A}_n(z)}{z}=\frac{(z-z_I)z_I}{z(z-z_I)}\hat{A}_L(z_I)\frac{1}{P_I^2}\hat{A}_R(z_I)|_{z=z_I}=\hat{A}_L(z_I)\frac{1}{P_I^2}\hat{A}_R(z_I)
    \end{equation*}
\end{frame}
